\section{Introduction}

What is linux filesystem api?
Why is it important
How many years it has been ParComputind
How it's learned today
Is an api older than the internet still documented well on qa websites
study shows that stackoverflow is the most visited
Others show its dymanics on recent API


documentation is hard to understand [ref]
Additionally, many POSIX functions share similar names, while others have different flags that change their behavior[example]

posix has known problems
this study complains about it and its security issues
Many blog posts alsocomplain about its usage
This is a way to quantify this stuff
'
Robillard study the decisions open source developers make while creating
developer documentation for frameworks and libraries [9]
s. They concluded that the community answers review, conceptual,
and how-to questions more frequently than any other type, with review questions
achieving a 92\% accepted answer rate [21]. Posnett et al. studied the nature of expertise
among Stack Exchange participants and found that participation in online Q/A sites
does not necessarily lead to increased expertise as measured by peer scoring [16]
Parnin and Treude study availability of documentation
across APIs within StackOverflow and find that it is very uneven, some APIs are well
covered, while others receive very little attention [20]. Jiau and Yang address this concern
and assert that more obscure API components benefit from a trickle down affect of
similar API components [11].
The work most similar to ours is recent work by Parnin et al. who also evaluated
the degree to which specific APIs are discussed within the community [15].
'
Theory?


\subsection{Research questions}
\begin{itemize}
  \item
  RQ1 Can we rely on the Stack Overflow crowd to discuss all of Linux kernel filesystem APIs?
  \begin{itemize}
    \item
    RQ1.1 Are the API methods widely covered?
    \item
    RQ1.2 Is there a relationship between number of discussions around a function and its usage in Github repositories?
    \item
    RQ1.3 Are there still ongoing discussions about these APIs? How fast are they covered?
  \end{itemize}
  \item
  RQ2 What kind of questions are asked about the APIs? Which keywords appear commonly among each group of filesystem APIS
  \item
  RQ3 How much cunfusion arises when discussing the APIs? To measure this, we ask: How often do questions compare between many different APIs?
\end{itemize}
